\Large \bf SIRIUS: A Revolutionary Approach to I/O and Storage for Exascale Scientific Computing

### 2016-03-11 papers/2016-HotStorage/paper.tex
added authors list

%for single author (just remove % characters)
\author{
{\rm Your N.\ Here}\\
Your Institution
\and
{\rm Second Name}\\
Second Institution
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

>>>>

%for single author (just remove % characters)
%\author{
%{\rm Your N.\ Here}\\
%Your Institution
%\and
%{\rm Second Name}\\
%Second Institution
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
%} % end author
%\numberofauthors{1}
\author{
Jay Lofstead\footnotemark[1]~~,
Hasan Abbasi\footnotemark[3]~~,
Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
Jong Choi\footnotemark[3]~~,
Matthew Curry\footnotemark[1]~~,\\
Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
Tahsin Kurc\footnotemark[9]~~,
Qing Liu\footnotemark[3]~~,
Jeremy Logan\footnotemark[4]~~,
Carlos Maltzahn\footnotemark[2]~~,
Manish Parashar\footnotemark[5]~~,\\
Norbert Podhorzski\footnotemark[3]~~,
Feiyi Wang\footnotemark[3]~~,
Matthew Wolf\footnotemark[7]~~,
C. S. Chang\footnotemark[8]~~,
Michael Churchill\footnotemark[8]~~,
Stephane Ethier\footnotemark[8]~~
\\
\footnotemark[1]~~Sandia National Laboratories,
\footnotemark[2]~~University of California Santa Cruz,\\
\footnotemark[3]~~Oak Ridge National Laboratory,
\footnotemark[4]~~U. Tenn. Knoxville,
\footnotemark[5]~~Rutgers University,\\
\footnotemark[6]~~Brown University,
\footnotemark[7]~~Georgia Tech,
\footnotemark[8]~~PPPL,
\footnotemark[9]~~Stony Brook
}
